Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-26 article.tex
bookmark

@@

A camera pixel collects light from a narrow cone in the
atmosphere. The cone includes some voxels, intersects with some other
voxels, and oblivious to all the rest~(\cref{fig:projection}b).
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
  \caption{\small [a] Irradiance of voxel $k$ is attenuated by voxels
    above it on a SR. The scattered radiance from voxel $k$ is then
    attenuated by voxels below it on a LOS to camera $c$.  [b] An
    image pixel captures light emanating in a cone in space. Voxels
    that fully or partially fall in this cone are sensed by the
    pixel.}
  \label{fig:projection}
\end{figure}
Thus light power captured at a pixel is a weighted sum of the power
$p_c(k)$ from all voxels.  This linear sum is formulated by a matrix
operation over ${\bm p}_c$. The measured image is column-stacked to a
vector $N_{\rm pix}$ long. It is given by
\begin{equation}
  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
  \;\;.
  \label{eq:IcP}
\end{equation}

>>>>

%An infinitesimal volume contains aerosols. The extinction and
%scattering coefficients due to aerosols in this volume are,
%respectively
%\begin{equation}
%  \beta^{\rm aerosol}=\sigma^{\rm aerosol} n^{\rm aerosol}
%  \;\;,\;\;
%  \alpha^{\rm aerosol}=\varpi^{\rm aerosol} \beta^{\rm aerosol}
%  \;.
%  \label{eq:betaer}
%\end{equation}
%The infinitesimal volume contain also air molecules. Hence, the
%overall extinction and scattering coefficients in this small volume
%are, respectively
%\begin{equation}
%  \beta=\beta^{\rm air}+\beta^{\rm aerosol}
%  \;\;,\;\;
%  \alpha=\alpha^{\rm air}+\alpha^{\rm aerosol}
%  \;.
%  \label{eq:betair}
%\end{equation}

@@

A camera pixel collects light from a narrow cone in the
atmosphere. The cone includes some voxels, intersects with some other
voxels, and oblivious to all the rest~(\cref{fig:projection}b).
%\begin{figure}
%  \centering
%  \yoavcomment{\def\svgwidth{0.8\columnwidth}\input{images/light_transfer.pdf_tex}}
%  \caption{\small [a] Irradiance of voxel $k$ is attenuated by voxels
%    above it on a SR. The scattered radiance from voxel $k$ is then
%    attenuated by voxels below it on a LOS to camera $c$.  [b] An
%    image pixel captures light emanating in a cone in space. Voxels
%    that fully or partially fall in this cone are sensed by the
%    pixel.}
%  \label{fig:projection}
%\end{figure}
Thus light power captured at a pixel is a weighted sum of the power
$p_c(k)$ from all voxels.  This linear sum is formulated by a matrix
operation over ${\bm p}_c$. The measured image is column-stacked to a
vector $N_{\rm pix}$ long. It is given by
\begin{equation}
  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
  \;\;.
  \label{eq:IcP}
\end{equation}
